\paperTitle

### 2014-05-17 doc/icml2014/background.tex
coarse pass over composite likelihood

% Maximum likelihood
The standard estimation procedure is maximum likelihood:
  \begin{align*}
    L_\text{unsup}(\theta) &\eqdef \sum_{\vx \in \sD} \log p_\theta(\vx)
        =  \sum_{\vx \in \sD} \log \sum_{\vh \in \sH} p_\theta(\vx,\vh).
  \end{align*}
  Maximum likelihood is statistically efficient,
  but in general computationally intractable
  because marginalizing over hidden variables $\vh$ yields a non-convex objective.
In practice, one uses local optimization procedures (e.g., EM
  or L-BFGS) on the marginal likelihood, but these can get stuck in local
  optima.
We will later return to likelihoods, but let us first
describe a method of moments approach for parameter estimation.
To do this, let's introduce some notation.

>>>>

% Maximum likelihood
The standard estimation procedure is maximum likelihood:
  \begin{align}
    \label{eqn:unsup}
    L_\text{unsup}(\theta) &\eqdef \sum_{\vx \in \sD} \log p_\theta(\vx)
        =  \sum_{\vx \in \sD} \log \sum_{\vh \in \sH} p_\theta(\vx,\vh).
  \end{align}
  Maximum likelihood is statistically efficient,
  but in general computationally intractable
  because marginalizing over hidden variables $\vh$ yields a non-convex objective.
In practice, one uses local optimization procedures (e.g., EM
  or L-BFGS) on the marginal likelihood, but these can get stuck in local
  optima.
We will later return to likelihoods, but let us first
describe a method of moments approach for parameter estimation.
To do this, let's introduce some notation.

### 2014-05-17 doc/icml2014/directed.tex
coarse pass over composite likelihood

\begin{figure}
  \centering
  \subfigure[Bottleneck] {
    \includegraphics[width=0.35\columnwidth]{figures/three-view.pdf}
    \label{fig:three-view}
  }
  \subfigure[Exclusive views]{
    \includegraphics[width=0.45\columnwidth]{figures/exclusive-views.pdf}
    \label{fig:exclusive-views}
  }

  \caption{
    \label{fig:bottleneckExclusiveViews}
  (a) A bottleneck can be estimated consistently
  using tensor factorization \citep{anandkumar13tensor}.
  (b) An example of exclusive views for a bi-dependent subset $S$.
  }
\end{figure}

@@

\begin{algorithm}
  \caption{\LearnMarginals~(pseudoinverse version)}
  \label{algo:learnMarginals}
  \begin{algorithmic}
    \REQUIRE Hidden subset $S = \{ h_{i_1}, \dots, h_{i_m} \}$ with exclusive views $\sV = \{ x_{v_1}, \dots, x_{v_m} \}$
    and conditional moments $\mOpp{v_j}{i_j} = \Pr(x_{v_i} \mid h_{i_j})$
    \ENSURE Marginals $Z_S = \Pr(\bh_S)$.
      %\STATE Identify exclusive views $\Sx{\sV} = \{x_{v_1}, \dots, x_{v_m}\}$.
      \STATE Return $\mH_S \gets \mO_{\sV}( \mOpp{v_1}{i_i}\pinv, \dots, {\mOpp{v_m}{i_m}}\pinv )$.
  \end{algorithmic}
\end{algorithm}

>>>>

\begin{figure}
  \centering
  \subfigure[Bottleneck] {
    \includegraphics[width=0.35\columnwidth]{figures/three-view.pdf}
    \label{fig:three-view}
  }
  \hspace{2em}
  \subfigure[Exclusive views]{
    \includegraphics[width=0.35\columnwidth]{figures/exclusive-views.pdf}
    \label{fig:exclusive-views}
  }

  \caption{
    \label{fig:bottleneckExclusiveViews}
  (a) A bottleneck can be estimated consistently
  using tensor factorization \citep{anandkumar13tensor}.
  (b) An example of exclusive views for a bidependent subset $S$.
  }
\end{figure}

@@

\begin{algorithm}
  \caption{\LearnMarginals~(pseudoinverse)}
  \label{algo:learnMarginals}
  \begin{algorithmic}
    \REQUIRE Hidden subset $S = \{ h_{i_1}, \dots, h_{i_m} \}$ with exclusive views $\sV = \{ x_{v_1}, \dots, x_{v_m} \}$
    and conditional moments $\mOpp{v_j}{i_j} = \Pr(x_{v_i} \mid h_{i_j})$.
    \ENSURE Marginals $Z_S = \Pr(\bh_S)$.
      %\STATE Identify exclusive views $\Sx{\sV} = \{x_{v_1}, \dots, x_{v_m}\}$.
      \STATE Return $\mH_S \gets \mO_{\sV}( \mOpp{v_1}{i_i}\pinv, \dots, {\mOpp{v_m}{i_m}}\pinv )$.
  \end{algorithmic}
\end{algorithm}
